conmat: generate synthetic contact matrices for a given age-stratified population

### 2024-07-17 paper/paper.Rmd
Updated implementation section
Updated abstract

There are currently few options to generate synthetic contact matrices with existing contact surveys. 
Existing methods to generate synthetic contact matrices are not designed for replicability, do not have enough granularity, and does not cover enough administrative areas (some countries are not included).

[ What's different and useful about conmat? ] 
A higher level of granularity however is sometimes required to make public health decisions for a given population.

@@

[ What else is covered in this paper? ] The implemented methods are tested and an example of its use is provided for a local government area (i.e. sub-national level) in Australia.

@@

@@

The six terms are the `|i-j|`,

The six key features of the relationship between the age groups, represented by the six terms, are displayed in the figure below.

```{r}
# use DHARMA to show a partial dep plot of the six main terms
```

Each cell in the resulting contact matrix, indexed *i*, *j*, is the predicted number of people in age group *j* that a single individual in age group *i* will have contact with per day. If you sum across all the *j* age groups for each *i* age group, you get the predicted total number of contacts per day for each individual of age group *i*. [ #TODO expected, predicted, or average? ]

[ #TODO notes-to-self: the model structure wasn't generated through any particularly robust process, it was just coming up with structures that looked mildly appropriate for our use case. ]

>>>>

There are currently few options for a user to generate their own synthetic contact matrices. 
Existing methods to generate synthetic contact matrices are not designed for replicability, do not have enough granularity, and does not cover enough administrative areas (in other words, some countries are not included).

[ What's different and useful about conmat? ] 
Users might have their own contact survey data that they would like to generate synthetic contact matrices from.
Perhaps the population demography is different, or the contact rates varying.
A higher level of granularity however is sometimes required to make public health decisions for a given population.

@@

[ What else is covered in this paper? ] The implemented methods are tested and an example of its use is provided for a local government area (i.e. at the sub-national level) in Australia.

@@

[ #TODO Is this also a heat map? ]

@@

Each cell in the resulting contact matrix, indexed *i*, *j*, is the predicted number of people in age group *j* that a single individual in age group *i* will have contact with per day. If you sum across all the *j* age groups for each *i* age group, you get the predicted total number of contacts per day for each individual of age group *i*. [ #TODO expected, predicted, or average? Does it matter? ]

The six terms are $|i-j|$, ${|i-j|}^{2}$, $i + j$, $i \times j$, $\text{max}(i, j)$ and $\text{min}(i, j)$.

The six key features of the relationship between the age groups, represented by the six terms, are displayed in the figure below. 
[ #TODO notes-to-self: the model structure wasn't generated through any particularly robust process, it was just coming up with structures that looked mildly appropriate for our use case. ]

```{r}
# Show partial dep plot of the six main terms
```
